Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-02-25 FIE2019.tex
Merged to IEEE style

%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
%\documentclass[sigconf]{acmart}
\documentclass[sigconf,anonymous]{acmart}
\usepackage{paralist}
\usepackage{url}
%\usepackage{enumitem}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

@@

%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

%%%% Proceedings format for SIGPLAN conferences 
% \documentclass[sigplan, anonymous, review]{acmart}

%%%% Proceedings format for SIGCHI conferences
% \documentclass[sigchi, review]{acmart}

\usepackage{booktabs} % For formal tables

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\copyrightyear{2019}
\acmYear{2019}
\setcopyright{acmlicensed}
\acmConference[ITiCSE '19]{The 24th Annual Conference on Innovation
  and Technology in Computer Science Education}{Jul. 15-17,
  2019}{Aberdeen, UK}
%\acmBooktitle{}
%\acmPrice{15.00}
%\acmDOI{10.1145/3159450.3159547}
%\acmISBN{978-1-4503-5103-4/18/02}
% This slight change to the code may also save 1 or 2 lines of space.

% removes the headers from each page per the preparation instructions, as these are not needed and will be updated with the chairs' actual session names during the pagination/indexing process:
\fancyhead{}

\begin{document}
\title{Cybersecurity Is Too Important To Be Left To The Specialists}
%\title{What Do We Mean By Cybersecurity Education?}  Tom's original

\author{Tom Crick}
\orcid{0000-0001-5196-9389}
\affiliation{%
  \institution{Swansea University}
  \streetaddress{}
  \city{Swansea} 
  \country{United Kingdom}
}
\email{thomas.crick@swansea.ac.uk}

\author{James H. Davenport}
\orcid{0000-0002-3982-7545}
\affiliation{%
  \institution{University of Bath}
  \streetaddress{}
  \city{Bath} 
  \country{United Kingdom}
}
\email{j.h.davenport@bath.ac.uk}

\author{Alastair Irons}
\orcid{}
\affiliation{%
  \institution{Sunderland University}
  \streetaddress{}
  \city{Sunderland} 
  \country{United Kingdom}
}
\email{alastair.irons@sunderland.ac.uk}

\author{Tom Prickett}
\orcid{}
\affiliation{%
  \institution{Northumbria University}
  \streetaddress{}
  \city{Newcastle upon Tyne} 
  \country{United Kingdom}
}
\email{tom.prickett@northumbria.ac.uk}

% The default list of authors is too long for headers}
%\renewcommand{\shortauthors}{Crick et al.}

@@

\keywords{TBC}

@@

This is not a brand-new concern: see \cite{Parr2014a} for concerns over five years ago, but it is a growing one. On the one hand, GDPR has increased the corporate penalties for failure, and therefore the demand for various forms of Cybersecurity specialists, both explicitly by requiring Data Protection Officers\footnote{\cite{EU292016a} places quite strong requirements on these: ``expertise in national and European data protection laws and practices and an in-depth understanding of the GDPR'', as well as ``principles of data processing'', ``data protection by design and by default'' and ``security of processing''. It is hard to envisage one person possessing all these attributes, and indeed ``DPO as a service'' is being promoted \cite{McCreanor2018d}.} and implicitly by causing boards to invest more in Cybersecurity. On the other hard, the growing publicity given to these, and the growing use of electronic payment, has also led to greater demand for staff in this area.
% JHD what are these?  Also the next paragraph needs thinking about

@@

\section*{Acknowledgements}
Thanks to Sally Pearce, Academic Accreditation Manager, BCS, The Chartered Institute for IT for supplying the summary information related to Accreditation.

\bibliographystyle{ACM-Reference-Format}
\bibliography{ITiCSE2019}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{paralist}
\usepackage{url}
\usepackage{enumitem}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[T1]{fontenc}
\usepackage{booktabs} % For formal tables

\usepackage{hyperref}

@@

\begin{document}

\title{Cybersecurity Is Too Important\\To Be Left To The Specialists}
%\title{What Do We Mean By Cybersecurity Education?}  Tom's original

% \author{\IEEEauthorblockN{Tom Crick}
% \IEEEauthorblockA{\textit{School of Education} \\
% \textit{Swansea University}\\
% Swansea, UK \\
% thomas.crick@swansea.ac.uk}
% \and
% \IEEEauthorblockN{James H. Davenport}
% \IEEEauthorblockA{\textit{Department of Computer Science} \\
% \textit{University of Bath}\\
% Bath, UK \\
% j.h.davenport@bath.ac.uk}
% \and
% \IEEEauthorblockN{Alastair Irons}
% \IEEEauthorblockA{\textit{Faculty of Technology} \\
% \textit{name of organization (of Aff.)}\\
% Sunderland University, Sunderland, UK\\
% alastair.irons@sunderland.ac.uk}
% \and
% \IEEEauthorblockN{Tom Prickett}
% \IEEEauthorblockA{\textit{School of Computing} \\
% \textit{name of organization (of Aff.)}\\
% Northumbria University, Newcastle upon Tyne, UK \\
% tom.prickett@northumbria.ac.uk}
% }

% compact IEEE author format for more than three authors...
\author{\IEEEauthorblockN{Tom Crick\IEEEauthorrefmark{1}, James
    H. Davenport\IEEEauthorrefmark{2}, Alastair
    Irons\IEEEauthorrefmark{3} and Tom Prickett\IEEEauthorrefmark{4}} 
\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Education, 
Swansea University, Swansea, UK; Email: thomas.crick@swansea.ac.uk} 
\IEEEauthorblockA{\IEEEauthorrefmark{2}Department of Computer Science, 
University of Bath, Bath, UK; Email: j.h.davenport@bath.ac.uk}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Faculty of Technology, 
Sunderland University, Sunderland, UK; Email: alastair.irons@sunderland.ac.uk}
\IEEEauthorblockA{\IEEEauthorrefmark{4}School of Computing, 
Northumbria University, Newcastle upon Tyne, UK; Email: tom.prickett@northumbria.ac.uk}}

@@

\begin{IEEEkeywords}
TBC
\end{IEEEkeywords}

@@

This is not a brand-new concern: see \cite{Parr2014a} for concerns over five years ago, but it is a growing one. On the one hand, GDPR has increased the corporate penalties for failure, and therefore the demand for various forms of Cybersecurity specialists, both explicitly by requiring Data Protection Officers\footnote{\cite{EU292016a} places quite strong requirements on these: ``expertise in national and European data protection laws and practices and an in-depth understanding of the GDPR'', as well as ``principles of data processing'', ``data protection by design and by default'' and ``security of processing''. It is hard to envisage one person possessing all these attributes, and indeed ``DPO as a service'' is being promoted \cite{McCreanor2018d}.} and implicitly by causing boards to invest more in Cybersecurity. On the other hard, the growing publicity given to these, and the growing use of electronic payment, has also led to greater demand for staff in this area.

@@

\section*{Acknowledgements}
Thanks to Sally Pearce, Academic Accreditation Manager, BCS--The
Chartered Institute for IT for supplying the summary information
related to Accreditation.

\bibliographystyle{IEEEtran}
\bibliography{FIE2019}
